|

### 2023-05-15 paper/03-methods.Rmd
Updated Strain citation.

In materials science, strain is the deformation of a material from stress, showing the rate of change in a material's length relative to its original length [@strain].
Formally, let $L(t)$ be the distance between any given two points of interest within a material at time $t$, and $L_0$ be the initial distance between those two points.
The **strain** for a material at time $t$ is defined as 
\begin{equation}
s(t)= \frac{L(t)-L_{0}}{L_{0}}.
\end{equation}
Notice that this measure is unitless due to being a ratio of two quantities having the same dimension.

>>>>

In materials science, strain is the deformation of a material from stress, showing the rate of change in a material's length relative to its original length [@callister2009materials].
Formally, let $L(t)$ be the distance between any given two points of interest within a material at time $t$, and $L_0$ be the initial distance between those two points.
The **strain** for a material at time $t$ is defined as 
\begin{equation}
s(t)= \frac{L(t)-L_{0}}{L_{0}}.
\end{equation}
Notice that this measure is unitless due to being a ratio of two quantities having the same dimension.
